---
title: "Challenge_2_SupervisedMLRegr"
author: "LukasMackel"
date: "2024-06-11"
output: html_document
---
This is the Markdown for the second Challenge in SuperVisedML Regression 2:

```{r}
#see manual
# Standard
library(tidyverse)

# Modeling
library(parsnip)

# Preprocessing & Sampling
library(recipes)
library(rsample)

# Modeling Error Metrics
library(yardstick)

# Plotting Decision Trees
library(rpart.plot)

```

```{r}
#First the modeling from the lecture document
# Modeling ----------------------------------------------------------------
bike_orderlines_tbl <- readRDS("bike_orderlines.rds")
glimpse(bike_orderlines_tbl)

model_sales_tbl <- bike_orderlines_tbl %>%
  select(total_price, model, category_2, frame_material) %>%
  
  group_by(model, category_2, frame_material) %>%
  summarise(total_sales = sum(total_price)) %>%
  ungroup() %>%
  
  arrange(desc(total_sales))

model_sales_tbl %>%
  mutate(category_2 = as_factor(category_2) %>% 
           fct_reorder(total_sales, .fun = max) %>% 
           fct_rev()) %>%
  
  ggplot(aes(frame_material, total_sales)) +
  geom_violin() +
  geom_jitter(width = 0.1, alpha = 0.5, color = "#2c3e50") +
  #coord_flip() +
  facet_wrap(~ category_2) +
  scale_y_continuous(labels = scales::dollar_format(scale = 1e-6, suffix = "M", accuracy = 0.1)) +
  tidyquant::theme_tq() +
  labs(
    title = "Total Sales for Each Model",
    x = "Frame Material", y = "Revenue"
  )
```


```{r}

# loading data samples
bike_features_tbl <- readRDS("~/bike_features_tbl.rds")
glimpse(bike_features_tbl)

# 2.0 TRAINING & TEST SETS ----
bike_features_tbl <- bike_features_tbl %>% 
  
  mutate(id = row_number()) %>% 
  
  select(id, everything(), -url)

```

```{r}
bike_features_tbl %>% distinct(category_2)

# run both following commands at the same time
set.seed(seed = 1113)
split_obj <- rsample::initial_split(bike_features_tbl, prop   = 0.80, 
                                                       strata = "category_2")

# Check if testing contains all category_2 values
split_obj %>% training() %>% distinct(category_2)
split_obj %>% testing() %>% distinct(category_2)

# Assign training and test data
train_tbl <- training(split_obj)
test_tbl  <- testing(split_obj)

# We have to remove spaces and dashes from the column names
train_tbl <- train_tbl %>% set_names(str_replace_all(names(train_tbl), " |-", "_"))
test_tbl  <- test_tbl  %>% set_names(str_replace_all(names(test_tbl),  " |-", "_"))
```

```{r}
# 3.1.1 Model ----
?lm # from the stats package
?set_engine
?fit # then click Estimate model parameters and then fit at the bottom

model_01_linear_lm_simple <- linear_reg(mode = "regression") %>%
    set_engine("lm") %>%
    fit(price ~ category_2 + frame_material, data = train_tbl)
```

Above is all partially the parts from the lecture content

----------------------------------------------

Challenge 2::
The next part will be my solution for the challenge 2 with the recipe package:

First a linear regression model is creates, that is similar to the one created in the manual. Then the recipe is created with the dummy given in the task itself. Then the testing and training data is created
```{r}
?recipe
?step_dummy
?prep
?bake

# making a new linear regression model
model_01_linear_lm_simple <- linear_reg(mode = "regression") %>%
    set_engine("lm") 

# creating a recipe object
recipe_obj <- recipe(price ~ frame_material + category_2 + model, data = bike_orderlines_tbl) %>% # function for the price predict from the given variables added
               #test
                step_dummy(all_nominal(),-frame_material,-category_2,-model,one_hot = T) %>% # Check out the argument one_hot = T
                prep() # estimate the required parameters

train_transformed_tbl <- bake(recipe_obj, new_data = train_tbl) # this creates a training data set
test_transformed_tbl  <- bake(recipe_obj, new_data = test_tbl) # this creates a testing data set

# including the workflow package
library(workflows)
# first create a workflow
workflow <- workflow(preprocessor = NULL, spec = NULL) %>% 
  workflows::add_recipe(recipe_obj) %>% # adding the created recipe object from before
  workflows::add_model(model_01_linear_lm_simple) # adding the created model from before

# now fit the workflow:
wf_fit <- fit(workflow, train_transformed_tbl) # this estimates the model param. of the training set

# now the yardstick part: 

metrics <- wf_fit %>%
           predict(new_data = test_transformed_tbl) %>% #predict from the testing data set from above
           bind_cols(test_transformed_tbl %>% select(price)) %>%
           yardstick::metrics(truth = price, estimate = .pred) %>% print() # and then print the yardstick metrics

``` 